---
title: "Reproducible Data Assignment 2"
author: "Jack Israel"
date: "07/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Loading and preprocessing the data
```{r loading-step, echo=FALSE, cache=TRUE}
library(dplyr)
library(ggplot2)
Data <- read.csv("activity//activity.csv")
```
First issue to note - some of the EVTYPE labels are inconsistently spelled, probably due to by-hand early entry. These will need to be processed to fit. Probably best to find/recreate the original list. 

May want to turn the BGN_DATE column to actual date-time objects

Principles of processing based on EVTYPE
* Remove 'summary' events
* Include 'record' events alongside their usual counterparts
* Aggregate all different spellings and variations of events into larger categories of weather events
* To create the categories, follow the principles laid out in the "NATIONAL WEATHER SERVICE INSTRUCTION 10-1605" document.

Here's a list of all the categories we will split EVTYPES into:

```{r Category List}

Low_Tide <- c("ASTRONOMICAL LOW TIDE")
```

```{r}
Avalanche <- c("AVALANCHE")
```

```{r}
"HEAVY SNOW/BLIZZARD/AVALANCHE"
```

```{r}
Blizzard <- c("BLIZZARD", "BLIZZARD WEATHER", "GROUND BLIZZARD", "BLIZZARD/FREEZING RAIN")
``` 

```{r}
Blizzard_High_Wind <- c("BLIZZARD/HIGH WIND", "HIGH WIND/ BLIZZARD", "HIGH WIND/BLIZZARD", "HIGH WIND/BLIZZARD/FREEZING RA")
```

```{r}
 "HIGH WIND/WIND CHILL/BLIZZARD"
```


```{r}
Blizzard_Heavy_Snow <- c("HEAVY SNOW/BLIZZARD", "BLIZZARD/HEAVY SNOW", "BLIZZARD AND HEAVY SNOW")
```

```{r}
Coastal_Flood <- c("BEACH FLOOD", "COASTAL FLOOD", "HEAVY SURF COASTAL FLOODING", "COASTAL FLOODING" , "COASTAL SURGE", "COASTAL/TIDAL FLOOD", "BEACH EROSION/COASTAL FLOOD",  "COASTALFLOOD", " COASTAL FLOOD", "COASTAL FLOODING/EROSION", "COASTAL EROSION", "COASTAL  FLOODING/EROSION")
``` 

```{r}
Coastal_Storm <- c("COASTAL STORM" , "COASTALSTORM")
```


```{r}
Wind_Chill_Blizzard <-  c("BLIZZARD AND EXTREME WIND CHIL")
```

```{r}
Cold_Wind_Chill <- c("WIND CHILL", "HIGH WIND/LOW WIND CHILL", "HIGH WINDS AND WIND CHILL", "WIND CHILL/HIGH WIND", "HIGH WIND/WIND CHILL", "SNOW- HIGH WIND- WIND CHILL", "LOW WIND CHILL", "COLD WIND CHILL TEMPERATURES", "BITTER WIND CHILL", "BITTER WIND CHILL TEMPERATURES")
```

```{r}
Debris_Flow <- c("TORNADO DEBRIS")
Dense_Fog <- c("DENSE FOG", "PATCHY DENSE FOG")
Dense_Smoke <- c("DENSE SMOKE")
Drought <- c("DROUGHT", "SNOW DROUGHT")
```

```{r}
Dust_Devil <- c("Dust Devil", "DUST DEVEL", "DUST DEVIL")
Dust_Storm <- c("Saharan Dust", "BLOWING DUST", "DUST STORM", "DUSTSTORM")
```

```{r}
Dust_Storm_High_Wind <- c("DUST STORM/HIGH WINDS", "HIGH WINDS DUST STORM")
```


```{r}
Heat_Drought <- c("HEAT WAVE DROUGHT", "HEAT/DROUGHT", "EXCESSIVE HEAT/DROUGHT", "HEAT DROUGHT")
```

```{r}
Heat <- c("Heatburst", "HEAT", "Record Heat", "EXTREME HEAT", "EXCESSIVE HEAT","RECORD HEAT", "RECORD HEAT WAVE", "RECORD/EXCESSIVE HEAT","HEAT WAVE", "HEAT WAVES")
# Review this
```


```{r}
Excessive_Heat_Drought <- c("EXCESSIVE HEAT/DROUGHT", "DROUGHT/EXCESSIVE HEAT")
```

```{r}
Extreme_Cold_Wind_Chill <-  c("EXTREME COLD",  "EXTREME/RECORD COLD", "Extreme Cold", "EXTREME COLD/WIND CHILL")  
```

```{r}
Extreme_Wind_Chill <- c("EXTREME WIND CHILLS", "EXTREME WIND CHILL", "EXTREME WIND CHILL/BLOWING SNO", "EXTREME WINDCHILL", "EXTREME WINDCHILL TEMPERATURES")
```


```{r}
Flash_Flood <- c("FLASH FLOOD", "FLASH FLOODING", "FLASH FLOODS", "FLOOD/FLASH FLOOD", "FLASH FLOOD WINDS", "FLASH FLOOD/", "LOCAL FLASH FLOOD", "FLOOD/FLASH FLOODING", "FLASH FLOOD/FLOOD", "FLASH FLOOD FROM ICE JAMS", "FLASH FLOOD/ STREET", "FLOOD FLASH", "FLOOD FLOOD/FLASH",  "FLOOD/FLASH", "FLASH FLOOD/ FLOOD", "FLASH FLOODING/FLOOD", "FLASH FLOOODING", "FLOOD/FLASHFLOOD", "FLASH FLOOD/LANDSLIDE", "FLASH FLOOD LANDSLIDES", "FLOOD/FLASH/FLOOD", " FLASH FLOOD")
```

```{r}
Flash_Flood_Heavy_Rain<- c("FLASH FLOOD - HEAVY RAIN", "FLASH FLOOD/HEAVY RAIN")
```

```{r}
Flood <- c("Ice jam flood (minor", "FLOODING", "FLOOD", "BREAKUP FLOODING", "RIVER FLOOD", "FLOOD WATCH/", "LOCAL FLOOD", "FLOOD/RAIN/WINDS", "STREAM FLOODING", "FLOOD/RAIN/WIND", "MINOR FLOODING", "SMALL STREAM FLOODING", "FLOODS", "RURAL FLOOD", "MAJOR FLOOD", "ICE JAM FLOODING", "STREET FLOOD", "SMALL STREAM FLOOD", "RIVER AND STREAM FLOOD", "MINOR FLOOD", "RIVER FLOODING", "FLOOD/RIVER FLOOD", "HAIL FLOODING", "TIDAL FLOOD", "HIGHWAY FLOODING", "SNOWMELT FLOODING", "STREET FLOODING", "TIDAL FLOODING")
```

```{r}
Heavy_Rain_Flood <- c("FLOODING/HEAVY RAIN", "HEAVY RAIN/FLOODING", "HEAVY RAIN AND FLOOD", "HEAVY RAINS/FLOODING", "HEAVY RAIN; URBAN FLOOD WINDS;", "FLOOD & HEAVY RAIN", "HEAVY RAIN/URBAN FLOOD")
```

```{r}
"HIGH WINDS/COASTAL FLOOD"
```

```{r}
Freezing_Fog <- c("FREEZING FOG")

Frost_Freeze <- c("FREEZE", "DAMAGING FREEZE", "AGRICULTURAL FREEZE", "HARD FREEZE", "EARLY FREEZE", "LATE FREEZE", "FROST", "FROST\\FREEZE", "RECORD COLD/FROST", "EARLY FROST", "COLD AND FROST", "FIRST FROST", "FROST/FREEZE", "Early Frost")

Funnel_Cloud <- c("FUNNEL CLOUD", "FUNNEL", "WALL CLOUD/FUNNEL CLOUD", "FUNNEL CLOUDS", "COLD AIR FUNNEL", "COLD AIR FUNNELS", "FUNNEL CLOUD.", "FUNNELS")
```

```{r}
"FUNNEL CLOUD/HAIL"
```

```{r}
Hail <- c("small hail", "HAIL", "HAIL 1.75)", "HAIL STORM", "HAIL 75", "SMALL HAIL", "HAIL 80", "HAIL 0.75", "HAIL 1.00", "HAIL/WINDS", "HAIL/WIND", "HAIL 1.75", "WIND/HAIL", "HAIL 225", "HAIL 0.88", "DEEP HAIL", "HAIL 88", "HAIL 175", "HAIL 100", "HAIL 150", "HAIL 075", "HAIL 125", "HAIL 200", "HAIL FLOODING", "HAIL DAMAGE", "HAIL 088", "HAIL/ICY ROADS", "HAIL ALOFT", "HAIL 275", "HAIL 450", "HAILSTORM", "HAILSTORMS", "TSTM WIND/HAIL", "GUSTY WIND/HAIL", "LATE SEASON HAIL", "NON SEVERE HAIL")
```


```{r}
Heavy_Rain <- c("HEAVY RAIN", "HEAVY RAINS", "HEAVY RAIN/SEVERE WEATHER", "HEAVY RAIN; URBAN FLOOD WINDS;", "HEAVY RAINFALL",  "HEAVY RAIN/SMALL STREAM URBAN", "HEAVY RAIN/WIND", "LOCALLY HEAVY RAIN", "HEAVY RAIN EFFECTS")
```



```{r}
Heavy_Snow <- c("HEAVY SNOW", "HEAVY SNOWPACK", "HEAVY SNOW/BLOWING SNOW", "SNOW AND HEAVY SNOW", "SNOW/HEAVY SNOW", "HEAVY SNOW/FREEZING RAIN", "HEAVY SNOW AND ICE", "HEAVY SNOW ANDBLOWING SNOW", "HEAVY SNOW/ICE", "HEAVY SNOW SQUALLS", "HEAVY SNOW/SQUALLS", "HEAVY SNOW-SQUALLS", "HEAVY SNOW   FREEZING RAIN", "HEAVY SNOW & ICE", "HEAVY SNOW AND")
```


```{r}
High_Surf <- c("Heavy surf and wind", "HEAVY SURF COASTAL FLOODING", "HEAVY SURF", "HIGH SURF", "ROUGH SURF"  , "HIGH SURF ADVISORY", "   HIGH SURF ADVISORY", "HAZARDOUS SURF", "HIGH SURF ADVISORIES", "HEAVY SURF/HIGH SURF")
```

```{r}
Rip_Currents_Heavy_Surf <- c("RIP CURRENTS HEAVY SURF", "RIP CURRENTS/HEAVY SURF")
```

```{r}
High_Wind <- c("HIGH WINDS", "HIGH WIND", "HIGH WIND AND HIGH TIDES", "RECORD COLD AND HIGH WIND", "HIGH WIND/SEAS", "HIGH WIND DAMAGE", "HIGH WINDS 57", "HIGH WINDS 66", "HIGH WINDS 76", "HIGH WINDS 63", "HIGH WINDS 67", "HIGH WINDS 82", "HIGH WINDS 80", "HIGH WINDS 58", "HIGH WINDS 73", "HIGH WINDS 55", "HIGH WINDS/", "HIGH WIND 63", "HIGH WIND 70", "HIGH WINDS/COLD", "SNOW/HIGH WINDS", "HIGH WINDS/SNOW", "HIGH WIND AND SEAS", "HIGH WIND 48", "HIGH WIND (G40)", "MARINE HIGH WIND")
```
 

```{r}
High_Wind_Heavy_Snow <- c("HIGH WIND AND HEAVY SNOW", "HIGH WIND/HEAVY SNOW", "HEAVY SNOW/HIGH WINDS", "HEAVY SNOW/HIGH WIND", "HEAVY SNOW AND HIGH WINDS", "HEAVY SNOW/WIND", "HEAVY SNOW/HIGH")
```


```{r}
High_Wind_Wind_Chill <- c("HIGH WIND/LOW WIND CHILL", "HIGH WINDS AND WIND CHILL", "WIND CHILL/HIGH WIND", "HIGH WIND/WIND CHILL")

High_Wind_Heavy_Rain <- c("HIGH WINDS HEAVY RAINS", "HIGH WINDS/HEAVY RAIN")
```


```{r}
"SNOW- HIGH WIND- WIND CHILL"
```


```{r}
Hurricane_Typhoon <- c("HURRICANE OPAL/HIGH WINDS", "HURRICANE ERIN", "HURRICANE OPAL", "HURRICANE", "HURRICANE-GENERATED SWELLS", "HURRICANE EMILY", "HURRICANE GORDON", "HURRICANE FELIX", "TYPHOON", "HURRICANE/TYPHOON")
```
Common sense ruling - Hurricane/Typhoon is more dominant than just High Wind

```{r}
Ice_Storm <- c("ICE STORM", "SNOW AND ICE STORM", "ICE STORM AND SNOW", "GLAZE/ICE STORM", "SNOW/ICE STORM")
```

```{r}
Heavy_Snow_Ice_Storm <- c("HEAVY SNOW/ICE STORM", "HEAVY SNOW AND ICE STORM")
```

```{r}
"HEAVY SNOW/WINTER STORM"
```

```{r}
"ICE STORM/FLASH FLOOD"
```


```{r}
Lake_Flood <- c("LAKESHORE FLOOD", "LAKE FLOOD")
```

```{r}
Lake_Effect_Snow <- "LAKE-EFFECT SNOW"
```

```{r}
Lightning <- c("LIGHTNING", "LIGHTNING INJURY", "LIGHTNING.", "LIGHTNING FIRE", "LIGHTNING DAMAGE", "LIGHTNING AND WINDS", "LIGHTNING  WAUSEON", " LIGHTNING")
```

```{r}
Heavy_Rain_Lightning <- c("LIGHTNING AND HEAVY RAIN", "HEAVY RAIN/LIGHTNING",     "LIGHTNING/HEAVY RAIN")
```

```{r}
Marine_Hail <- "MARINE HAIL"
```

```{r}
Rip_Currents <- c("RIP CURRENT", "RIP CURRENTS")
```

```{r}
Seiche <- "SEICHE"
```

```{r}
Sleet <- c("SLEET", "LIGHT SNOW AND SLEET", "FREEZING RAIN AND SLEET",       "SLEET/RAIN/SNOW", "SNOW/RAIN/SLEET", "SNOW/SLEET/FREEZING RAIN", "FREEZING RAIN/SLEET", "SNOW/SLEET", "FREEZING RAIN SLEET AND", "FREEZING RAIN SLEET AND LIGHT", "SLEET & FREEZING RAIN","SNOW SLEET", "SLEET/SNOW", "SNOW/SLEET/RAIN", "SLEET/FREEZING RAIN", "SNOW AND SLEET", "SLEET STORM", "Snow and sleet")   
```



```{r}
"HEAVY SNOW/SLEET"
"SLEET/ICE STORM"
```


```{r}
Strong_Wind <- c("Strong Wind", "Strong Winds", "Flood/Strong Wind", "STRONG WINDS", "STRONG WIND", "ICE/STRONG WINDS", "STRONG WIND GUST", "MARINE STRONG WIND")
```

```{r}
"HEAVY SNOW AND STRONG WINDS"
```

```{r}
Storm_Tide <- c("STORM SURGE/TIDE")
```


```{r}
"MARINE THUNDERSTORM WIND"
```


```{r}
Thunderstorm_Hail <- c("THUNDERSTORM WINDS/HAIL", "THUNDERSTORM WINDS HAIL", "THUNDERSTORM WINDS/ HAIL", "THUNDERSTORM HAIL", "THUNDERSTORM WINDSHAIL", "THUNDERSTORM WIND/HAIL")
```

```{r}
Thunderstorm_Lightning <- c("THUNDERSTORM WINDS LIGHTNING", "TSTM WIND AND LIGHTNING",  "LIGHTNING THUNDERSTORM WINDSS", "LIGHTNING THUNDERSTORM WINDS", "LIGHTNING AND THUNDERSTORM WIN", "THUNDERSTORM WIND/LIGHTNING")
```

```{r}
Thunderstorm_Funnel_Cloud <- c("THUNDERSTORM WINDS/FUNNEL CLOU", "THUNDERSTORM WINDS FUNNEL CLOU")
```

```{r}
Thunderstorm_Heavy_Rain <- c("THUNDERSTORM WINDS/HEAVY RAIN", "THUNDERSTORM WINDS HEAVY RAIN", "TSTM HEAVY RAIN")
```

```{r}
Flood_Thunderstorm <- c("THUNDERSTORM WINDS URBAN FLOOD", "THUNDERSTORM WINDS/FLOODING", "THUNDERSTORM WINDS/ FLOOD")
```

```{r}
Flash_Flood_Thunderstorm <- c("FLASH FLOODING/THUNDERSTORM WI", "THUNDERSTORM WINDS/FLASH FLOOD")
```


```{r}
Tornado <- c("TORNADO", "TORNADO F0", "TORNADOS", "COLD AIR TORNADO", "TORNADO F3", "TORNADO F1", "TORNADO F2", "TORNADOES")
```

```{r}
"TSUNAMI"
```

```{r}
Volcanic_Ash <- c("VOLCANIC ASH", "VOLCANIC ASHFALL", "Volcanic Ash", "Volcanic Ash Plume")
```

```{r}
"VOLCANIC ERUPTION"
```


```{r}
"TORNADOES, TSTM WIND, HAIL"
```


```{r}
Tropical_Storm <- c("TROPICAL STORM ALBERTO", "TROPICAL STORM","TROPICAL STORM GORDON", "TROPICAL STORM JERRY", "TROPICAL STORM DEAN")
```

```{r}
Tropical_Depression <- "TROPICAL DEPRESSION"
```

```{r}
Waterspout <- c("WATERSPOUT", "WATERSPOUTS", "WATERSPOUT-", " WATERSPOUT", "WATERSPOUT/")
```

```{r}
Waterspout_Tornado <- c("WATERSPOUT/TORNADO", "WATERSPOUT TORNADO", "WATERSPOUT-TORNADO", "TORNADO/WATERSPOUT") 
```

```{r}
"DUST DEVIL WATERSPOUT"
"WATERSPOUT FUNNEL CLOUD"
```

```{r}
Wildfire <- c("WILDFIRE", "WILDFIRES", "WILD FIRES", "WILD/FOREST FIRE")
```

```{r}
Cold <- c("cold", "COLD")
```

```{r}
Mudslides <- c()
```


```{r}
Winter_Storm_High_Wind <- c("WINTER STORM/HIGH WIND", "WINTER STORM/HIGH WINDS","WINTER STORM HIGH WINDS")
```

```{r}
Winter_Storm <- c("WINTER STORM", "WINTER STORMS")
```

```{r}
Winter_Weather <- c("WINTER WEATHER", "WINTER WEATHER MIX", "WINTER WEATHER/MIX", "WINTER MIX")
```

```{r}
Urban_Flood <- c()

```

```{r}
Thunderstorm_Wind <- c("TUNDERSTORM WIND", "THUNDERSTORM WINDS", "THUNDERSTORM WIND", "THUNDERSTORM WINS", "THUNDERSTORM", "SEVERE THUNDERSTORM", "SEVERE THUNDERSTORMS", "SEVERE THUNDERSTORM WINDS", "THUNDERSTORMS WINDS", "THUNDERSTORMS", "THUNDERSTORM WINDS 60", "THUNDERSTORM WINDSS", "THUNDERSTORM WINDS53", "THUNDERSTORM WINDS 13", "THUNDERSTORM WINDS SMALL STREA", "THUNDERSTORM WINDS 2", "THUNDERSTORM WINDS 61", "THUNDERSTORM DAMAGE", "THUNDERSTORMW 50", "THUNDERSTORMS WIND", "THUNDERSTORM  WINDS", "THUNDERSTORM WIND G50", "THUNDERSTORM WINDS      LE CEN", "THUNDERSTORM WINDS G", "THUNDERSTORM WIND G60", "THUNDERSTORM WINDS.", "THUNDERSTORM WIND G55", "THUNDERSTORM WINDS G60", "THUNDERSTORM WINDS 62", "THUNDERSTORM WINDS 53", "THUNDERSTORM WIND 59", "THUNDERSTORM WIND 52", "THUNDERSTORM WIND 69", "THUNDERSTORMW WINDS", "THUNDERSTORM WIND 60 MPH", "THUNDERSTORM WIND 65MPH", "THUNDERSTORM WIND/ TREES", "THUNDERSTORM WIND/AWNING", "THUNDERSTORM WIND 98 MPH", "THUNDERSTORM WIND TREES", "THUNDERSTORM WIND 59 MPH", "THUNDERSTORM WINDS 63 MPH", "THUNDERSTORM WIND/ TREE", "THUNDERSTORM DAMAGE TO", "THUNDERSTORM WIND 65 MPH", "THUNDERSTORM WIND.", "THUNDERSTORM WIND 59 MPH.", "THUNDERSTORM WINDS AND", "THUNDERSTORM WINDS 50", "THUNDERSTORM WIND G52", "THUNDERSTORM WINDS 52", "THUNDERSTORM WIND G51", "THUNDERSTORM WIND G61", "THUNDERSTORM W INDS", "THUNDERSTORM WIND 50", "THUNDERSTORM WIND 56", "THUNDERSTORMW", "THUNDERSTORMWINDS", "THUNDERSTORM WIND (G40)", "GUSTY THUNDERSTORM WINDS", "GUSTY THUNDERSTORM WIND", "TSTM WIND", "TSTM WIND 51", "TSTM WIND 50", "TSTM WIND 52", "TSTM WIND 55", "TSTM WIND G58", "TSTM WIND DAMAGE", "TSTM WINDS", "TSTMW", "TSTM WIND 65)", "TSTM WIND (G45)", "TSTM WIND 40", "TSTM WIND 45", "TSTM WIND (41)", "TSTM WIND (G40)", "TSTM WND", " TSTM WIND", " TSTM WIND (G45)", "TSTM WIND  (G45)", "TSTM WIND (G35)", "TSTM" , "TSTM WIND G45", "NON-TSTM WIND", "NON TSTM WIND")
```

```{r}
Categories <- c()


```



```{r Reprocessing the Data}
X1 <- X1 %>% mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Blizzard, "Blizzard")) %>% 
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Blizzard_Heavy_Snow, "Blizzard & Heavy Snow")) %>% 
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Blizzard_High_Wind, "Blizzard & High Wind")) %>% 
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Coastal_Flood, "Coastal Flood")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Coastal_Storm, "Coastal Storm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Cold_Wind_Chill, "Cold/Wind Chill")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Dense_Fog, "Dense Fog")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Drought, "Drought")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Dust_Devil, "Dust Devil")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Dust_Storm, "Dust Storm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Dust_Storm_High_Wind, "Dust Storm/High Wind")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Excessive_Heat_Drought, "Excessive Heat/Drought")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Extreme_Cold_Wind_Chill, "Extreme Cold/Wind Chill")) %>%mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heat, "Heat")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heat_Drought, "Heat/Drought")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Flash_Flood, "Flash Flood")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Flash_Flood_Heavy_Rain, "Flash Flood/Heavy Rain")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Flash_Flood_Thunderstorm, "Flash Flood/Thunderstorm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Flood, "Flood")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Flood_Thunderstorm, "Flood/Thunderstorm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Frost_Freeze, "Frost/Freeze")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Funnel_Cloud, "Funnel Cloud")) %>%
    mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Hail, "Hail")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heat_Drought, "Heat/Drought")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heavy_Rain, "Heavy Rain")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heavy_Rain_Flood, "Heavy Rain/Flood")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heavy_Rain_Lightning, "Heavy Rain/Lightning")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heavy_Snow, "Heavy Snow")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Heavy_Snow_Ice_Storm, "Heavy Snow/Ice Storm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% High_Surf, "High Surf")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% High_Wind, "High Wind")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% High_Wind_Heavy_Rain, "High Wind/Heavy Rain")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% High_Wind_Heavy_Snow, "High Wind/Heavy Snow")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% High_Wind_Wind_Chill, "High Wind/Wind Chill")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Hurricane_Typhoon, "Hurricane/Typhoon")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Ice_Storm, "Ice Storm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Lake_Flood, "Lake Flood")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Lightning, "Lightning")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Rip_Currents, "Rip Currents")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Rip_Currents_Heavy_Surf, "Rip Current/Heavy Surf")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Sleet, "Sleet")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Strong_Wind, "Strong Wind")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Thunderstorm_Wind, "Thunderstorm Wind")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Thunderstorm_Hail, "Thunderstorm/Hail")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Thunderstorm_Lightning, "Thunderstorm/Lightning")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Thunderstorm_Heavy_Rain, "Thunderstorm/Heavy Rain")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Tornado, "Tornado")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Tropical_Storm, "Tropical Storm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Volcanic_Ash, "Volcanic Ash")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Waterspout, "Waterspout")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Waterspout_Tornado, "Waterspout/Tornado")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Wildfire, "Wildfire")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Wind_Chill_Blizzard, "Wind Chill/Blizzard")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Winter_Storm, "Winter Storm")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Winter_Storm_High_Wind, "Winter Storm/High Wind")) %>%
  mutate(EVTYPE = replace(EVTYPE, EVTYPE %in% Winter_Weather, "Winter Weather"))
```












